---
title: "Supplementary Materials: Bird diversity and community varies with proximity to trails in urban and peri-urban green spaces"
format:
  html:
    embed-resources: true
    fig-width: 16
    fig-height: 14
  docx:
    fig-width: 12
    fig-height: 14
---

Chloe A. Cull^1^, Mackenzie Guest^1^, Isabella C. Richmond^1^, Ana Morales^2^, Carly D. Ziter^1^, Barbara Frei^1,2^

1 Department of Biology, Concordia University, Montreal, QC, Canada

2 Science and Technology Branch, Environment and Climate Change Canada, Montreal, QC, Canada

**Statement of Ethics Compliance** All details of animal monitoring were approved by Concordia University’s Animal Care Facility (Protocol no. 30017925) and by The Canadian Wildlife Service (Permit no. SC-98).

```{r}
#| label: setup
#| include: false


knitr::opts_chunk$set(echo = F)
options(tidyverse.quiet = T)

library(targets)
tar_source('R')
```

# Supplementary Materials A: Model Equations

## Model 1: distance from trail + management

The models contained both distance from trail (close vs far) and park management (formal vs informal):

$$y_i \sim \alpha_{park} + \beta_0 +  far_i*\beta_{far} + informal_i*\beta_{informal} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

<!-- -->

- $\alpha$ and $\beta_0$ both represent intercepts, $\alpha$ is used for random effects and $\beta_0$ for fixed effects

- Parkrepresents the park where the measurements took place

- Far represents one of the distance categories from the trail (i.e., close vs far)

- Informal represents one of the management categories (i.e., formal vs informal)

- $\epsilon_i$ represents residual error

## Model 2: stem density

The models contained both stem density and the interaction between distance to trail and stem density:

$$y_i \sim \alpha_{park} + \gamma_{distance} + stem \ dens_i*\beta_{stem \ dens} + stem \ dens_i*\beta_{distance} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

- $\alpha$ and $\gamma$ both represent intercepts, $\alpha$ is used for random effects and $\gamma$ for fixed interaction effects

- Park represents the park where the measurements took place

- Distance represents the distance from the trail (i.e., close vs far)

- Stem dens represents the stem density of the transect

- $\epsilon_i$ represents residual error

## Model 3: basal area

The models contained both basal area and the interaction between distance to trail and basal area :

$$y_i \sim \alpha_{park} + \gamma_{distance} + basal \ area_i*\beta_{basal \ area} + basal \ area_i*\beta_{distance} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

- $\alpha$ and $\gamma$ both represent intercepts, $\alpha$ is used for random effects and $\gamma$ for fixed interaction effects

- Park represents the park where the measurements took place

- Distance represents the distance from the trail (i.e., close vs far)

- Basal area represents the basal area of the transect

- $\epsilon_i$ represents residual error

## Model 4: trail activity

The models contained both average trail activity and the interaction between distance to trail and average trail activity:

$$y_i \sim \alpha_{park} + \gamma_{distance} + activity_i*\beta_{activity} + activity_i*\beta_{distance} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

- $\alpha$ and $\gamma$ both represent intercepts, $\alpha$ is used for random effects and $\gamma$ for fixed interaction effects

- Park represents the park where the measurements took place

- Distance represents the distance from the trail (i.e., close vs far)

- Activity represents the average human activity level on the trail

- $\epsilon_i$ represents residual error


# Supplementary Materials B: Model Diagnostic Plots 

```{r}
#| label: dist-sr

tar_load(SR_dist_model)

check_model(SR_dist_model)
```

Figure B1. Model diagnostic plot where species richness is the response variable and distance to trail and greenspace management type are explanatory variables.


```{r}
#| label: dist-shan

tar_load(shan_dist_model)

check_model(shan_dist_model)
```
Figure B2. Model diagnostic plot where Shannon diversity is the response variable and distance to trail and greenspace management type are explanatory variables.

```{r}
#| label: veg-sr

tar_load(SR_veg_model)

check_model(SR_veg_model)
```
Figure B3. Model diagnostic plot where species richness is the response variable and stem density and the interaction between stem density and distance to trail are the explanatory variables.


```{r}
#| label: veg-shan

tar_load(shan_veg_model)

check_model(shan_veg_model)
```
Figure B4. Model diagnostic plot where Shannon diversity is the response variable and stem density and the interaction between stem density and distance to trail are the explanatory variables.


```{r}
#| label: bas-sr

tar_load(SR_basal_model)

check_model(SR_basal_model)
```
Figure B5. Model diagnostic plot where species richness is the response variable and basal area and the interaction between basal area and distance to trail are the explanatory variables.


```{r}
#| label: bas-shan

tar_load(shan_basal_model)

check_model(shan_basal_model)
```
Figure B6. Model diagnostic plot where Shannon diversity is the response variable and basal area and the interaction between basal area and distance to trail are the explanatory variables.


```{r}
#| label: act-sr

tar_load(SR_act_model)

check_model(SR_act_model)
```
Figure B7. Model diagnostic plot where speciess richness is the response variable and human activity and the interaction between human activity and distance to trail are the explanatory variables.

```{r}
#| label: act-shan

tar_load(shan_act_model)

check_model(shan_act_model)
```
Figure B8. Model diagnostic plot where Shannon diversity is the response variable and human activity and the interaction between human activity and distance to trail are the explanatory variables.


# Supplementary Materials C: Ordination Results

Table C1. Relationship between environmental variables and NMDS ordination space for formal sites. 

```{r}
#| label: ord-env
tar_load(env_ordination)

```

