---
title: "Model Diagnostics"
format:
  html:
    embed-resources: true
    fig-width: 14
    fig-height: 14
  pdf:
    fig-width: 12
    fig-height: 14
---

Chloe A. Cull, Mackenzie Guest, Isabella C. Richmond, Ana Morales, Carly D. Ziter, Barbara Frei 



```{r}
#| label: setup
#| include: false


knitr::opts_chunk$set(echo = F)
options(tidyverse.quiet = T)

library(targets)
tar_source('R')
```

# Model Results

## Model 1: distance from trail + management 

The models contained both distance from trail (close vs far) and park management (formal vs informal): 

$$
y_i \sim \beta_0 + far_i*\beta_{far} + informal_i*\beta_{informal} + \epsilon_i
$$
$y_i$ was modelled as both species richness and Shannon. 

### Species Richness

```{r}
#| label: dist-sr

tar_load(SR_dist_model)

check_model(SR_dist_model)
```

### Shannon 

```{r}
#| label: dist-shan

tar_load(shan_dist_model)

check_model(shan_dist_model)
```

## Vegetation 

### Species Richness

### Shannon 

## Trail use 

### Species Richness

### Shannon 
