---
title: "Model Diagnostics"
format:
  html:
    embed-resources: true
    fig-width: 16
    fig-height: 14
---

Chloe A. Cull, Mackenzie Guest, Isabella C. Richmond, Ana Morales, Carly D. Ziter, Barbara Frei

```{r}
#| label: setup
#| include: false


knitr::opts_chunk$set(echo = F)
options(tidyverse.quiet = T)

library(targets)
tar_source('R')
```

# Model Results

## Model 1: distance from trail + management

The models contained both distance from trail (close vs far) and park management (formal vs informal):

$$y_i \sim \alpha_{park} + \beta_0 +  far_i*\beta_{far} + informal_i*\beta_{informal} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

<!-- -->

- $\alpha$ and $\beta_0$ both represent intercepts, $\alpha$ is used for random effects and $\beta_0$ for fixed effects

- Parkrepresents the park where the measurements took place

- Far represents one of the distance categories from the trail (i.e., close vs far)

- Informal represents one of the management categories (i.e., formal vs informal)

- $\epsilon_i$ represents residual error

### Species Richness

```{r}
#| label: dist-sr

tar_load(SR_dist_model)

check_model(SR_dist_model)
```

### Shannon

```{r}
#| label: dist-shan

tar_load(shan_dist_model)

check_model(shan_dist_model)
```

## Model 2: stem density

The models contained both stem density and the interaction between distance to trail and average trail activity:

$$y_i \sim \alpha_{park} + \gamma_{distance} + stem \ dens_i*\beta_{stem \ dens} + stem \ dens_i*\beta_{distance} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

- $\alpha$ and $\gamma$ both represent intercepts, $\alpha$ is used for random effects and $\gamma$ for fixed interaction effects

- Park represents the park where the measurements took place

- Distance represents the distance from the trail (i.e., close vs far)

- Stem dens represents the stem density of the transect

- $\epsilon_i$ represents residual error

### Species Richness

```{r}
#| label: veg-sr

tar_load(SR_veg_model)

check_model(SR_veg_model)
```

### Shannon

```{r}
#| label: veg-shan

tar_load(shan_veg_model)

check_model(shan_veg_model)
```

## Model 3: trail activity

The models contained both average trail activity and the interaction between distance to trail and average trail activity:

$$y_i \sim \alpha_{park} + \gamma_{distance} + activity_i*\beta_{activity} + activity_i*\beta_{distance} + \epsilon_i$$

- $y_i$ was modelled as both species richness and Shannon.

- $\alpha$ and $\gamma$ both represent intercepts, $\alpha$ is used for random effects and $\gamma$ for fixed interaction effects

- Park represents the park where the measurements took place

- Distance represents the distance from the trail (i.e., close vs far)

- Activity represents the average human activity level on the trail 

- $\epsilon_i$ represents residual error

### Species Richness

```{r}
#| label: act-sr

tar_load(SR_act_model)

check_model(SR_act_model)
```

### Shannon

```{r}
#| label: act-shan

tar_load(shan_act_model)

check_model(shan_act_model)
```
