---
title: "Bird diversity and community varies with proximity to trails in urban and peri-urban green spaces"
format:
  html:
    embed-resources: true
    fig-width: 14
    fig-height: 14
  pdf:
    fig-width: 12
    fig-height: 14
---

Chloe A. Cull, Mackenzie Guest, Isabella C. Richmond, Ana Morales, Carly D. Ziter, Barbara Frei 

```{r}
#| label: setup
#| include: false


knitr::opts_chunk$set(echo = F)
options(tidyverse.quiet = T)

library(targets)
tar_source('R')
```

# Model Results

## Model 1: distance from trail + greenspace management 

The first model includes both distance from trail and management. It does not include an interaction in the statistical analysis due to small sample size but a plot is included for context. 

### Species Richness 

Model summary: 

```{r}
#| label: sr-dist-summary

tar_load(SR_dist_model)

tbl_regression(SR_dist_model, label = list(form = "Management", dist = "Distance From Trail"))

```



Visualization: 

```{r}
#| label: sr-dist-plot

tar_load(bird_div)
sr <- bird_div %>% filter(div == "SR")

d <- ggplot(data = sr, aes(x = dist, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Species Richness") + 
	theme_classic()

m <- ggplot(data = sr, aes(x = form, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Species Richness") + 
	theme_classic()

i <- ggplot(data = sr, aes(x = form, y = val, colour = dist)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_point(position = position_jitterdodge()) + 
	labs(x = "", y = "Species Richness", colour = "") + 
	theme_classic() + 
	theme(legend.position = 'top') + 
	scale_color_viridis_d(end = 0.5)

(d / m) | i

```

### Shannon 

Model summary: 

```{r}
#| label: shan-dist-summary

tar_load(shan_dist_model)

tbl_regression(shan_dist_model, label = list(form = "Management", dist = "Distance From Trail") )

```


Visualization: 
```{r}
#| label: shan-dist-plot

tar_load(bird_div)
sh <- bird_div %>% filter(div == "Shan")

d <- ggplot(data = sh, aes(x = dist, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Shannon") + 
	theme_classic()

m <- ggplot(data = sh, aes(x = form, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Shannon") + 
	theme_classic()

i <- ggplot(data = sh, aes(x = form, y = val, colour = dist)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_point(position = position_jitterdodge()) + 
	labs(x = "", y = "Shannon", colour = "") + 
	theme_classic() + 
	theme(legend.position = 'top') + 
	scale_color_viridis_d(end = 0.5)

(d / m) | i

```

## Vegetation 

## Trail use 
