---
title: "Bird diversity and community varies with proximity to trails in urban and peri-urban green spaces"
format:
  html:
    embed-resources: true
  docx:
    fig-width: 12
    fig-height: 14
---

Chloe A. Cull, Mackenzie Guest, Isabella C. Richmond, Ana Morales, Carly D. Ziter, Barbara Frei
add_p
```{r}
#| label: setup
#| include: false


knitr::opts_chunk$set(echo = F)
options(tidyverse.quiet = T)

library(targets)
tar_source('R')

tar_load(full_data)
```

::: callout-tip
## Main Takeaways

-   SR & Shannon higher in informal sites

-   SR & Shannon higher further from trails
:::

# Model Results

## Model 1: distance from trail + greenspace management

The first model includes both distance from trail and management. It does not include an interaction in the statistical analysis due to small sample size but a plot is included for context.

Model summary:

```{r}
#| label: sr-dist-summary

tar_load(SR_dist_model)
tar_load(shan_dist_model)

modelsummary(list("Species Richness" = SR_dist_model, "Shannon Diversity" = shan_dist_model),
             fmt = NULL,
             estimate = "{signif(estimate, 2)}",
             exponentiate = c(FALSE, FALSE), 
             statistic = c("CI" = "({signif(conf.low, 2)}, {signif(conf.high, 2)})", 
                           "t-statistic" =  "{signif(statistic, 2)}", 
                           "p-value" = "{signif(p.value, 1)}"),
             conf_level = .95,
             gof_map = c("adj.r.squared", "adj.r.squared"),
             coef_rename = c("forminformal" = "Informal",
                             "distancefar" = "Far from trail"))


```

Visualization:

```{r}
#| label: sr-dist-plot

tar_load(bird_div)
sr <- bird_div %>% filter(div == "SR")
sh <- bird_div %>% filter(div == "Shan")

d <- ggplot(data = sr, aes(x = dist, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Species Richness") + 
	theme_classic()

m <- ggplot(data = sr, aes(x = form, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Species Richness") + 
	theme_classic()


d_sh <- ggplot(data = sh, aes(x = dist, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Shannon") + 
	theme_classic()

m_sh <- ggplot(data = sh, aes(x = form, y = val)) + 
	geom_boxplot(outlier.shape = NA) + 
	geom_jitter() + 
	labs(x = "", y = "Shannon") + 
	theme_classic()

(d | m) / (d_sh | m_sh) + plot_annotation(tag_levels = 'a') + plot_layout(guides = 'collect')

```



## Vegetation

The second model includes stem density and the interaction between stem density and distance from trail.


```{r}
#| label: sr-veg-summary

tar_load(SR_veg_model)
tar_load(shan_veg_model)


modelsummary(list("Species Richness" = SR_veg_model, "Shannon Diversity" = shan_veg_model),
             fmt = NULL,
             estimate = "{signif(estimate, 2)}",
             exponentiate = c(FALSE, FALSE), 
             statistic = c("CI" = "({signif(conf.low, 2)}, {signif(conf.high, 2)})", 
                           "t-statistic" =  "{signif(statistic, 2)}", 
                           "p-value" = "{signif(p.value, 1)}"),
             conf_level = .95,
             gof_map = c("adj.r.squared", "adj.r.squared"),
             coef_rename = c("stem_dens" = "Stem Density",
                             "stem_dens:distancefar" = "Stem density : Far from trail"))


```

```{r}
#| label: sr-veg-plot
#| warning: false
#| message: false

stemdens <- interaction_plot(SR_veg_model, 'stem_dens', x = stem_dens, y = SR, dat = full_data, xlab = 'Stem Density (stems/m2)', ylab = 'Species Richness')

stemdens_dist <- interaction_plot(SR_veg_model, c('stem_dens', 'distance'), colour = distance, x = stem_dens, y = SR, dat = full_data, xlab = 'Stem Density (stems/m2)', ylab = 'Species Richness')

stemdens_s <- interaction_plot(shan_veg_model, 'stem_dens', x = stem_dens, y = Shan, dat = full_data, xlab = 'Stem Density (stems/m2)', ylab = 'Shannon Diversity')

stemdens_dist_s <- interaction_plot(shan_veg_model, c('stem_dens', 'distance'), colour = distance, x = stem_dens, y = Shan, dat = full_data, xlab = 'Stem Density (stems/m2)', ylab = 'Shannon Diversity')


(stemdens_s | stemdens_dist_s) / (stemdens | stemdens_dist) + plot_annotation(tag_levels = 'a') + plot_layout(guides = 'collect')


```


## Trail use

The third model includes human activity and the interaction between human activity and distance from trail.


```{r}
#| label: sr-act-summary

tar_load(SR_act_model)
tar_load(shan_act_model)

modelsummary(list("Species Richness" = SR_act_model, "Shannon Diversity" = shan_veg_model),
             fmt = NULL,
             estimate = "{signif(estimate, 2)}",
             exponentiate = c(FALSE, FALSE), 
             statistic = c("CI" = "({signif(conf.low, 2)}, {signif(conf.high, 2)})", 
                           "t-statistic" =  "{signif(statistic, 2)}", 
                           "p-value" = "{signif(p.value, 1)}"),
             conf_level = .95,
             gof_map = c("adj.r.squared", "adj.r.squared"),
             coef_rename = c("stem_dens" = "Stem Density",
                             "stem_dens:distancefar" = "Stem density : Far from trail"))

tbl_regression(SR_act_model, label = list(avg_activity = "Human Activity",
																					distance = "Distance From Trail", 
																					 `Park.sd__(Intercept)` = "Random Effect: Park (Std Dev)",
																					 `Residual.sd__(Observation)` = "Random Effect: Residual (Std Dev)"),
							 pvalue_fun = label_style_pvalue(digits = 2),
							 tidy_fun = broom.mixed::tidy)

```

```{r}
#| label: sr-act-plot
#| warning: false
#| message: false

act <- interaction_plot(SR_act_model, 'avg_activity', x = avg_activity, y = SR, dat = full_data, xlab = 'Human Activity (mean number of people/hr)', ylab = 'Species Richness')

act_dist <- interaction_plot(SR_act_model, c('avg_activity', 'distance'), colour = distance, x = avg_activity, y = SR, dat = full_data, xlab = 'Human Activity (mean number of people/hr)', ylab = 'Species Richness')

act | act_dist
```

### Shannon

```{r}
#| label: shan-act-summary



tbl_regression(shan_act_model, label = list(avg_activity = "Human Activit", 
																						distance = "Distance From Trail", 
																					 `Park.sd__(Intercept)` = "Random Effect: Park (Std Dev)",
																					 `Residual.sd__(Observation)` = "Random Effect: Residual (Std Dev)"),
							 pvalue_fun = label_style_pvalue(digits = 2),
							 tidy_fun = broom.mixed::tidy)

```

```{r}
#| label: shan-act-plot
#| warning: false
#| message: false

act_s <- interaction_plot(shan_act_model, 'avg_activity', x = avg_activity, y = Shan, dat = full_data, xlab = 'Human Activity (mean number of people/hr)', ylab = 'Shannon Diversity')

act_dist_s <- interaction_plot(shan_act_model, c('avg_activity', 'distance'), colour = distance, x = avg_activity, y = Shan, dat = full_data, xlab = 'Human Activity (mean number of people/hr)', ylab = 'Shannon Diversity')

act_s | act_dist_s
```
